Descriptive_Stats

### 2023-09-26 Code/RankComparison.Rmd
Changed to a million permutations
Re-ran numbers for B = 1 million

```{r}
library(clusrank)
clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds")

clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds",
                exact = TRUE, B = 10000)
```

The code below reads in the data comparing the 2019 and 2022 World Championships.
```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Athlete", "Year")
#View(comp)
```

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (1 if 2019 and 2 if 2022).
```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds",
                exact = TRUE, B = 10000)
```

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (2 if 2022 and 3 if 2023).
```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds",
                exact = TRUE, B = 10000)
```

@@

>>>>

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds")

clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds",
                exact = TRUE, B = 1000000)
```

The code below reads in the data comparing the 2019 and 2022 World Championships.
```{r}
old_clusrank <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(old_clusrank) <- c("Time", "Athlete", "Year")
#View(comp)
```

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (1 if 2019 and 2 if 2022).
```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_clusrank,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_clusrank,
                method = "ds",
                exact = TRUE, B = 1000000)
```

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (2 if 2022 and 3 if 2023).
```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds",
                exact = TRUE, B = 1000000)
```

@@

```{r}
women_data <- read.csv("../Data/WomenClusrank2019vs2022.csv")
colnames(women_data) <- c("Time", "Athlete", "Year")
```

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds", 
                exact = TRUE, B = 1000000)
```
